% 参考文献
\def\line{−\hspace*{-.7zw}−}

\begin{thebibliography}{99}
%\bibitem{*}内の * は各自わかりやすい名前などをつけて、
%論文中には \cite{*} のように使用する。
%これをベースに書き換えた方が楽かも。
%書籍、論文、URLによって若干書き方が異なる。
%URLを載せる人は参考にした年月日を最後に記入すること。

\bibitem{qaoa} Bingzhi Zhang, Akira Sone, and Quntao Zhuang. Quantum computational phase transition in combinatorial problems. \textit{npj Quantum Information}, Vol. 8, No. 1, pp. 87, 2022.
\bibitem{quantum_annealing} Tadashi Kadowaki and Hidetoshi Nishimori. Quantum anneaing in the transverse ising model. \textit{Phys. Rev. E}, Vol. 58, pp. 5355-5363, Nov 1998.
\bibitem{murata} T.Murata. Petri nets: Properties, analysis and applications. \textit{Proceedings of the IEEE}, Vol. 77, No. 4, pp. 541-580, 1989.
\bibitem{cpn} Kurt Jenson, Lars Michael Kristensen, and Lisa Wells. Coloured Petri Nets and CPN Tools for modeling and validation of concurrent systems. \textit{International Journal on Software Tools for Technology Transfer}, Vol. 9, No. 3, pp. 213-254, 2007.
\bibitem{nouri} Houssem Eddine Nouri, Olfa Belkahla Driss, and Khaled Ghedira. Solving the flexible job shop problem by hybrid metahcuristics-based multiagent model. \textit{Journal on Software Tools fot Technology Transfar}, Vol. 9, No. 3, pp. 213-254, 2007.
\bibitem{osaka} 大阪大学医学部 Python会. Parameter Tuning - 大阪大学医学部 Python会. \url{https://oumpy.github.io/blog/2018/09/parameter_tuning.html}.
\bibitem{james} Bergstra, James, Daniel Yamins, and David Cox. Making a science of model search: Hyperparameter optimization in hundreds of dimensions for vision architectures. \textit{International conference on machine learning}, pp. 115-123, 2013.
\bibitem{shinjo} 新城巧也，名嘉村盛和，猪谷宜彦. 信学技報, 段替え作業を考慮したフローショップスケジューリング問題のペトリネットモデリングとQUBO 定式化. vol. 122, no. 78, MSS2022-17, pp. 90-95, 2022 年6 月
\bibitem{openjij} OpenJij.OpenJij - Optimization Library. \url{https://www.openjij.org}.

\end{thebibliography}
